An Executable Formal Semantics For A Functional Actor Language

### 2017-12-19 paper/paper.tex
modified intro, moved related work to own section, wrote configuration section

\subsection{Related Work}

\begin{figure}
          \centering
          \includegraphics[scale=0.13]{../k-overview.png}
	  \caption{Backend tools K provides from just an operational
            semantics. Some tools such as a semantics-based compiler and
            test-case generation are in progress.}
          \label{fig:k-tools}
\end{figure}
To demonstrate the power of K, languages as complex as C, Java, and JavaScript
have been fully defined using the K framework~\cite{ , , }. On top of that, in
all of these languages and more, nontrivial programs have been formally verified
using K's prover, such as proofs involving AVL trees and red-black trees. We
would like to add an actor-based language to the growing list of languages
defined in K, so we can take advantage of K's formal verification engine and
more.

@@

\section{The Actor Language in K}

\subsection{Configuration}

@@

\subsection{Semantics}

>>>>

In the rest of the paper we discuss related work, then the actor semantics in
some detail, including the configuration, the syntax and how we handle reduction
contexts in K, the semantics, and an in-depth example. We then conclude and
discuss future work.

\section{Related Work}

\begin{figure}
          \centering
          \includegraphics[scale=0.13]{../k-overview.png}
	  \caption{Backend tools K provides from just an operational
            semantics. Some tools such as a semantics-based compiler and
            test-case generation are in progress.}
          \label{fig:k-tools}
\end{figure}
To demonstrate the power of K, languages as complex as C, Java, and JavaScript
have been fully defined using the K framework~\cite{c,java,jscript}. On top of that, in
all of these languages and more, nontrivial programs have been formally verified
using K's prover, such as proofs involving AVL trees and red-black trees. We
would like to add an actor-based language to the growing list of languages
defined in K, so we can take advantage of K's formal verification engine and
more.

@@

\section{The Actor Language in K}
In this section, we describe in detail some important features of the actor
language from~\cite{}. We cover some important features from K and how they were
used to define key concepts of the actor language.

\subsection{Configuration}
All languages in K use a configuration to specify the current state of a
program. For simple languages like the lambda calculus or a simple \texttt{IMP}
language, there may only be one cell to hold the current computation (the
\texttt{k} cell) and perhaps another \texttt{env} cell for the current
environment. For the actor language, we have the following configuration:
\begin{verbatim}
configuration 
  <T>
    <actors>
      <actor multiplicity="*">     // a multiset of actors
        <k> exec($PGM:Exp) </k>    // actor state
        <id> initactor </id>       // actor id
      </actor>
    </actors>
    <messages>
      <message  multiplicity="*">  // a multiset of messages
        .K
      </message>
    </messages>
    <definedaddr>                  // list of defined actors'
      ListItem(initactor)          // addresses
    </definedaddr>
  </T>
\end{verbatim}
In addition to defining the state of a program, the configuration is also used
to define the initial state of a program. Initially, we only have one actor,
with the unique identifier \texttt{initactor}. It also contains the program in
the \texttt{exec} state ready to be executed. The variable \texttt{\$PGM} comes
from an external file. The notation \texttt{multiplicity=*} is used to specify
that there can be any number of \texttt{actor} cells and \texttt{message} cells
as a multiset of actors and messages respectively. Initially there are no
messages, represented using K's builtin \texttt{.K}. Finally, the
\texttt{definedaddr} cell is used to keep track of addresses of defined
actors. We need to keep track of this for the side condition of some semantic
rules (see Section~\ref{sec:semantics}).

For our K definition, we only define a single actor system, so there are no
external actors or receptionists. To add these one can simply add these as
additional cells in the configuration, initialized to the empty list.

@@

\subsection{Semantics}\label{sec:semantics}
